(Deep) Induction for GADTs

### 2021-04-06 induction-paper/GADT-induction.tex
add lambda terms example

Add third example here.

@@

@@

\subsection{Third example introduced above}

@@

@@

Lambda normal form example.

%Still don't know which applications we might have

>>>>

@@

{\color{red} STLC example}

GADTs are expressive enough to represent, for example, the types and terms of the simply typed lambda calculus. 
We will use a variant of the STLC including a base type of Bool, and type constructors for arrow types and list types:

\begin{equation}\label{eq:eq_ltype}
\begin{array}{l}
\mathsf{data\, LType\,(a : Set) : Set\,where}\\
\mathsf{\;\;\;\;\;\;\;\;TBool :\, \exists (b : Set). \,Equal\,a\,(KBool\, b) \to LType\,a}\\
\mathsf{\;\;\;\;\;\;\;\;TArr\,\,\, :\, \exists (b : Set) (c : Set).\,Equal\,a\,(b \to c) \to LType\,b \to LType\,c \to LType\,a}\\
  \mathsf{\;\;\;\;\;\;\;\;TList\,\, :\, \exists (b : Set).\,Equal\,a\,(\List\,b) \to LType\,b \to LType\,a}
\end{array}
\end{equation}

The term calculus for this type system includes variables, abstraction, application, 
and also includes an introduction rule that takes a list of terms of type $\mathsf{b}$ and produces a term of type $\mathsf{List\,b}$.

\begin{equation}\label{eq:eq_lterm}
\begin{array}{l}
\mathsf{data\, LTerm\,(a : Set) : Set\,where}\\
\mathsf{\;\;\;\;\;\;\;\;Var\,\,\,\,\,\,:\, String \to LType\,a \to LTerm\,a} \\
\mathsf{\;\;\;\;\;\;\;\;Abs\,\,\,\,\,\, :\, \exists (b : Set) (c : Set).\,Equal\,a\,(b \to c) \to String 
      \to LType\,b \to LTerm\,c \to LTerm\,a}\\
  \mathsf{\;\;\;\;\;\;\;\;App\,\,\,\,\, :\, \exists (b : Set).\,LTerm (b \to a) \to LTerm\,b \to LTerm\,a}\\
  \mathsf{\;\;\;\;\;\;\;\;ListC\,\, :\, \exists (b : Set).\,Equal\,a\,(\List\,b) \to List\,(LTerm\,b) \to LTerm\,a}
\end{array}
\end{equation}

The type parameter for $\mathsf{LTerm}$ tracks the types of STLC terms. So the type $\mathsf{LTerm\,A}$ 
contains lambda terms of type $\mathsf{A}$. The $\mathsf{LType}$ GADT is used to encode the 
grammar of permissible types for this calculus.

Variables are represented as strings and are tagged with their type. 
The $\mathsf{Abs}$ constructor takes a name (string) and a type for the bound variable,
and a term of type $\mathsf{c}$ for the body of the abstraction.
The $\mathsf{App}$ constructor applies a term of type $\mathsf{b \to a}$ to a term of type $\mathsf{b}$, producing
a term of type $\mathsf{a}$. 
The $\mathsf{ListC}$ constructor takes a list of terms of type $\mathsf{b}$ and produces a term of type $\mathsf{List\,b}$.

@@

\subsection{(Deep) induction for $\mathsf{LTerm}$ }

@@

{\color{red} Use $\mathsf{Pair^{\wedge}}$ everywhere}

{\color{blue} Some notational conventions: I am using uppercase letters for elements of LType and 
lowercase letters for elements of LTerm. For example, $\mathsf{(T_b : LType \, b)}$ or $\mathsf{(t_c : LTerm \,c)}$.}

Now we will define an induction rule for the $\mathsf{LTerm}$ type defined in 
Equation~\ref{eq:eq_lterm}. To define this, we need liftings for both $\mathsf{LType}$ and
$\mathsf{LTerm}$. We will also need a lifting of predicates for arrow types, since arrow types appear in 
$\mathsf{LType}$ and $\mathsf{LTerm}$. The lifting for arrow types 
\[
  \mathsf{Arr^{\wedge} : \forall (a\, b : Set) \to (a \to Set) \to (b \to Set) \to (a \to b) \to Set}
\]
is defined as: 
\[
  \mathsf{Arr^{\wedge}\, a\, b\, Q_a\, Q_b\, f = \forall (x : a) \to Q_a\, x \to Q_b\, (f\, x)}
\]

\noindent
Now we can define the lifting for $\mathsf{LType}$, which has type 
\[
\mathsf{LType^{\wedge} : \forall (a : Set) \to (a \to Set) \to LType\,a \to Set}
\]
and is defined by pattern-matching as
\[
  \mathsf{LType^{\wedge}\,a\,Q_a\,(TBool\,b\,e) = \exists (Q_b : b \to Set) 
  \to Equal^{\wedge}\, a\, b\, Q_a\, (KBool^{\wedge} \,b \,Q_b) \,e}
\]
where $\mathsf{Q_a : a \to Set}$ and $\mathsf{e : Equal \,a \,(KBool\,b)}$,
and
\begin{multline*}
  \mathsf{LType^{\wedge}\,a\,Q_a\,(TArr\, b\, c\, e\, T_b\, T_c)} \\
\mathsf{=
\exists (Q_b : b \to Set) (Q_c : c \to Set)
  \to Equal^{\wedge}\,a\, (b \to c)\, Q_a\, (Arr^{\wedge} \, b\, c\, Q_b \, Q_c) \, e} \\ 
\mathsf{
  \times \, LType^{\wedge}\,b\,Q_b\,T_b \times LType^{\wedge}\,c\,Q_c\,T_c
}
\end{multline*}

where $\mathsf{Q_a : a \to Set}$, $\mathsf{e : Equal\, a\, (b \to c)}$, $\mathsf{T_b : LType \,b}$, and 
$\mathsf{T_c : LType \,c}$,
and 
\begin{multline*}
  \mathsf{LType^{\wedge}\,a\,Q_a\,(TList\, b\, e\, T_b)} \\
\mathsf{=
\exists (Q_b : b \to Set) 
  \to Equal^{\wedge}\,a\, (List\, b)\, Q_a\, (List^{\wedge} \, b\, Q_b) \, e 
  \times LType^{\wedge}\,b\,Q_b\,T_b 
}
\end{multline*}

Given the lifting for $\mathsf{LType}$, we can define the lifting for $\mathsf{LTerm}$. Again, 
the lifting 
\[
\mathsf{LTerm^{\wedge} : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set}
\]
is defined by pattern-matching as
\[
  \mathsf{LTerm^{\wedge}\,a\,Q_a\,(Var\,s\,T_a) = LType^{\wedge}\, a\, Q_a\, T_a}
\]
where $\mathsf{s : String}$ and $\mathsf{T_a : LType\, a}$,  and 
\begin{multline*}
  \mathsf{LTerm^{\wedge}\,a\,Q_a\,
  (Abs \,b \,c \,e \,s \,T_b \,t_c)} \\ 
\mathsf{
  = \exists (Q_b : b \to Set) (Q_c : c \to Set) \to
      Equal^{\wedge} \, a\, (b \to c)\, Q_a\, (Arr^{\wedge} \, b\, c\, Q_b \, Q_c)\, e} \\ 
\mathsf{
      \times \, LType^{\wedge}\, b\, Q_b\, T_b
      \times \, LTerm^{\wedge}\, c\, Q_c\, t_c }
\end{multline*}
where $\mathsf{e : Equal \, a \, (b \to c)}$, $\mathsf{s : String}$ , $\mathsf{T_b : LType\,b}$, and $\mathsf{t_c : LTerm \, c}$,

and 
\begin{multline*}
  \mathsf{LTerm^{\wedge}\,a\,Q_a\, (App\, b\, t_{ba}\, t_b)} \\ 
\mathsf{
  = \exists (Q_b : b \to Set) \to 
      LTerm^{\wedge}\, (b \to a)\, (Arr^{\wedge} \, b\, a\, Q_b \, Q_a)\, t_{ba}
      \times LTerm^{\wedge}\, b\, Q_b\, t_b }
\end{multline*}

where $\mathsf{t_{ba} : LTerm \, (B \to A)}$ and $\mathsf{t_b : LTerm \, B}$, and
\begin{multline*}
  \mathsf{LTerm^{\wedge}\,a\,Q_a\, (ListC\, b\, e\, ts)} \\ 
\mathsf{
  = \exists (Q_b : b \to Set) \to 
      Equal^{\wedge} \, a\, (List\,b)\, Q_a\, (List^{\wedge} \, b\, Q_b) \, e
      \times List^{\wedge}\, (LTerm\,b) \, (LTerm^{\wedge} \, b\, Q_b) \, ts
    }
\end{multline*}

where $\mathsf{e : Equal\, a\, (List \,b)}$ and $\mathsf{ts : List\, (LTerm b)}$. 
Notice we use the lifting for $\mathsf{List}$ in the case for the $\mathsf{ListC}$ constructor.

With these liftings, we can define the deep induction princple for $\mathsf{LTerm}$.

% Var case 
Let CVar be the type 
\begin{multline*}
\mathsf{\forall (P : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set)} \\
\mathsf{\to 
  \forall (a : Set) (Q_a : a \to Set) (s : String) (T_a : LType\, a) 
  \to LType^{\wedge} \, a\, Q_a\, T_a
  \to P \, a\, Q_a\, (Var \, s\, T_a)
  }
\end{multline*}
associated to the $\mathsf{Var}$ constructor.

% Abs case 
Let CAbs be the type 
\begin{align*}
  &\mathsf{\forall (P : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set)} \\
  &\mathsf{\to 
  \forall (a \,b\, c: Set) (Q_a : a \to Set)  (Q_b : b \to Set) (Q_c : c \to Set)
  (e : Equal\, a\, (b \to c)) (s : String) } \\ 
  &\mathsf{ \to (T_b : LType\, b) \to (t_c : LTerm\, c)
  \to Equal^{\wedge}\,a\,(b \to c)\, Q_a \, (Arr^{\wedge} \, b\, c\, Q_b \, Q_c) \, e
  } \\
  &\mathsf{
  \to LType^{\wedge}\, b\, Q_b\, T_b
  \to P\, c\, Q_c\, t_c\, 
  \to P \, a\, Q_a\, (Abs \,b \,c \, e \,s \,T_b \, t_c)
  }
\end{align*}
associated to the $\mathsf{Abs}$ constructor.

% App case 
Let CApp be the type 
\begin{align*}
  &\mathsf{\forall (P : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set)} \\
  &\mathsf{\to 
  \forall (a \,b : Set) (Q_a : a \to Set)  (Q_b : b \to Set) 
   (t_{ba} : LTerm\, (b \to a)) (t_b : LTerm\, b)} \\
  &\mathsf{
  \to P\, (b \to a)\, (Arr^{\wedge} \, b\, a\, Q_b \, Q_a) \, t_{ba} \, 
  \to P\, b\, Q_b\, t_b\, 
  \to P \, a\, Q_a\, (App \,b \,t_{ba} \, t_b) }
\end{align*}
associated to the $\mathsf{App}$ constructor.

% ListC case 
Let CListC be the type 
\begin{align*}
  &\mathsf{\forall (P : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set)} \\
  &\mathsf{\to 
  \forall (a \,b : Set) (Q_a : a \to Set)  (Q_b : b \to Set) 
    (e : Equal\, a\, (List\, b)) (ts : List\, (LTerm\, b))} \\ 
  &\mathsf{
    \to Equal^{\wedge}\, a\, (List\,b)\, Q_a\, (List^{\wedge}\, b\, Q_b)\, e 
  \to List^{\wedge}\, (LTerm\,b) (P\, b\, Q_b)\, ts} \\
&\mathsf{
  \to P \, a\, Q_a\, (ListC \,b \,e \, ts) }
\end{align*}
associated to the $\mathsf{ListC}$ constructor.

Then the type of the deep induction principle for $\mathsf{LTerm}$ is,
\begin{multline*}
\mathsf{\forall (P : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set)}
\mathsf{\to CVar\,P \to CAbs\,P \to CApp\,P \to CListC\,P} \\
\mathsf{\to \forall (a : Set)(Q_a : a \to Set)(t_a : LTerm\,a) \to LTerm^{\wedge}\,a\,Q_a\,t_a \to P\,a\,Q_a\,t_a}
\end{multline*}

To prove the induction principle, we define a term $\mathsf{DILTerm}$ for it. We have to define 
\[ 
\mathsf{DILTerm \, P\, cvar \, cabs\, capp\, clistc \, a\, Q_a\, t_a\, L_a : P\, a\, Q_a\, t_a}
\]
% where $\mathsf{P : \forall (a : Set) \to (a \to Set) \to LTerm\,a \to Set}$,

As before, we prove the induction principle by pattern matching on $\mathsf{t_a}$.

For the $\mathsf{Var}$ case, let $\mathsf{t_a = Var\, s\, T_a}$ and define
\[
  \mathsf{DILTerm \, P\, cvar \, cabs\, capp\, clistc \, a\, Q_a\, (Var\,s\,T_a) \, L_a = cvar \, a\, Q_a\, s\, T_a\, L_a }
\]
% where $\mathsf{L_a : LTerm^{\wedge}\, a\, Q_a\, (Var\,s\,T_a)}$, i.e., $\mathsf{L_a : LType^{\wedge}\,a\,Q_a\,T_a}$ 
Notice that $\mathsf{LTerm^{\wedge}\, a\, Q_a\, (Var\,s\,T_a) = LType^{\wedge}\,a\,Q_a\,T_a}$, so 
$\mathsf{L_a : LType^{\wedge}\,a\,Q_a\,T_a}$.

% Abs case 
For the $\mathsf{Abs}$ case, let $\mathsf{t_a = (Abs \,b \,c \, e \,s \,T_b \, t_c)} $ and define
\begin{multline*}
  \mathsf{DILTerm \, P\, cvar \, cabs\, capp\, clistc \, a\, Q_a\, (Abs \,b \,c \,e \,s \,T_b \, t_c) \, (Q_b , Q_c , L_e, L_{T_b}, L_{t_c})} \\
  \mathsf{= cabs\,a\,b\,c\, Q_a\, Q_b\, Q_c\, e\, s\, T_b\, t_c\, L_e\, L_{T_b}\, p_c}
\end{multline*}

where $\mathsf{(Q_b , Q_c , L_e, L_{T_b}, L_{t_c}) : LTerm^{\wedge}\, a\, Q_a\, (Abs \,b \,c \, e \,s \,T_b \, t_c)}$
\begin{itemize}
  \item $\mathsf{Q_b : b \to Set}$
  \item $\mathsf{Q_c : c \to Set}$
  \item $\mathsf{L_e : Equal^{\wedge} \, a\, (b \to c)\, Q_a\, (Arr^{\wedge} \, b\, c\, Q_b \, Q_c) \, e}$
  \item $\mathsf{L_{T_b}: LType^{\wedge} \, b\, Q_b\, T_b}$
  \item $\mathsf{L_{t_c}: LTerm^{\wedge} \, c\, Q_c\, T_c}$
\end{itemize}

and $\mathsf{pc}$ is defined as:
\[
  \mathsf{pc =  DILTerm\,P\,cvar\,cabs \,capp \,clistc\, c\, Q_c\, t_c\, L_{t_c}  : P \, c\, Q_c \, t_c }
\]

% App case - (App \,b \,t_{ba} \, t_b)
For the $\mathsf{App}$ case, let $\mathsf{t_a = (App \,b \,\,t_{ba} \, t_b)} $ and define
\begin{multline*}
  \mathsf{DILTerm \, P\, cvar \, cabs\, capp\, clistc \, a\, Q_a\,  (App \,b \,\,t_{ba} \, t_b)\, (Q_b , L_{t_{ba}}, L_{t_b})} \\
  \mathsf{= capp\,a\,b\,Q_a\, Q_b\, t_{ba}\, t_b\, p_{ba} \, p_b}
\end{multline*}

where $\mathsf{(Q_b , L_{t_{ba}}, L_{t_b}) : LTerm^{\wedge}\, a\, Q_a\, (App \,b \,t_{ba} \, t_b)}$
\begin{itemize}
  \item $\mathsf{Q_b : b \to Set}$
  \item $\mathsf{L_{t_{ba}}: LTerm^{\wedge} \, (b \to a)\, (Arr^{\wedge} \, b\, a\, Q_b \, Q_a)\, t_{ba}}$
  \item $\mathsf{L_{t_b}: LTerm^{\wedge} \, b\, Q_b\, t_b}$
\end{itemize}

and $\mathsf{p_{ba}}$
and 
$\mathsf{p_b}$
and are defined as:
\begin{align*}
  \mathsf{p_{ba}} &=  \mathsf{DILTerm\,P\,cvar\,cabs \,capp \,clistc\, (b \to a)\,(Arr^{\wedge} \, b\, a\, Q_b \, Q_a) \, t_{ba}\, L_{t_{ba}}   : P \, (b \to a)\, (Arr^{\wedge} \, b\, a\, Q_b \, Q_a) \, t_{ba} } \\
  \mathsf{p_b   } &=  \mathsf{DILTerm\,P\,cvar\,cabs \,capp \,clistc\, b\, Q_b\, t_b\, L_{t_b}  : P \, b\, Q_b \, t_b } 
\end{align*}

% ListC case - (ListC \,b \,e \, ts)
For the $\mathsf{ListC}$ case, let $\mathsf{t_a = (ListC \,b \,e \, ts)} $ and define
\begin{multline*}
  \mathsf{DILTerm \, P\, cvar \, cabs\, capp\, clistc \, a\, Q_a\, (ListC \,b \,e \, ts) \, (Q_b , L_e, L_{List})
  = clistc \,a\,b\,Q_a\, Q_b\, e\, ts\, L_e\, p_{List} }
\end{multline*}

where $\mathsf{(Q_b , L_e, L_{List}): LTerm^{\wedge}\, a\, Q_a\, (ListC \,b \,e \, ts)}$
\begin{itemize}
  \item $\mathsf{Q_b : b \to Set}$
  \item $\mathsf{L_e : Equal^{\wedge}\, a\, (List\,b)\, Q_a\, (List^{\wedge}\, b\, Q_b)\, e}$
  \item $\mathsf{L_{List}: List^{\wedge} \, (LTerm\, b) \, (LTerm^{\wedge}\, b\, Q_b) \, ts}$
\end{itemize}

and $\mathsf{p_{List}}$ is defined as:
\begin{multline*}
  \mathsf{p_{List} = List^{\wedge}map \, (LTerm\, b) \, (LTerm^{\wedge} \, b \, Q_b)\, 
    (P\,b\,Q_b)\, \,p_{ts} \,\, ts\,\, L_{List}  : List^{\wedge}\, (LTerm\,b) \, (P\,b\,Q_b) \, ts}
\end{multline*}

where $\mathsf{p_{ts}}$ is defined as:

{\color{red} PredMap not defined yet} 
\begin{multline*}
  \mathsf{
  p_{ts} = DILTerm\, P\, cvar\, cabs\, capp\, clistc\, b\, Q_b :  PredMap \,(LTerm^{\wedge}\, b\, Q_b) \, (P\,b\,Q_b)
  }
\end{multline*}

@@

{\color{red} Compare with structural induction? or at least state why structural induction fails }

In this section we use deep induction for the $\mathsf{LTerm}$ GADT to 
extract the type from a lambda term. 
We have a predicate 
\begin{align*}
  &\mathsf{getType : \forall \, (a : Set) \to (t : LTerm\,a) \to Set} \\
  &\mathsf{getType \,a \,t = Maybe \, (LType \, a)}
\end{align*}

and we want to show this predicate is satisfied for every element of $\mathsf{LTerm\,a}$.
Because of the $\mathsf{ListC}$ constructor, this cannot be achieved without 
deep induction. In particular, deep induction is required to apply the induction to the 
individual terms in a list of terms.

So, using deep induction, we want to prove: 
\[
  \mathsf{getTypeProof : \forall \, (a : Set) \to (t : LTerm\,a) \to getType \,a \,t} \\
\]
which we prove by 
\[
  \mathsf{getTypeProof \,a \,t = 
    DILTerm\, (\lambda \, b\, Q_b\, t\, \to getType \,b\, t) \,
    gtVar\,  gtABs\,  gtApp\,  gtListC\,  x\,\, K1\,\, t\, (LTerm^{\wedge}K1\, x\, t)
    }
\]
where $\mathsf{K1 : x \to Set}$ and $\mathsf{LTerm^{\wedge}K1\, x\, t : LTerm^{\wedge}\, x\, K1\, t}$.
Notice that there is no space in $\mathsf{LTerm^{\wedge}K1}$, because
\[
  \mathsf{LTerm^{\wedge}K1 : \forall (a : Set) (t : LTerm A) \to LTerm^{\wedge}\, a\, K1\,t}
\]
is a function that we will define. In addition to defining $\mathsf{LTerm^{\wedge}K1}$,
we also have to give a proof for each constructor $\mathsf{Var, Abs, App, ListC}$:

\begin{multline*}
  \mathsf{gtVar : \forall (a : Set) (Q_a : a \to Set) (s : String) (T_a : LType\, a) 
      \to LType^{\wedge} \, a\, Q_a\, T_a\, \to Maybe\, (LType\, a)}
\end{multline*}

% abs 
\begin{multline*}
    \mathsf{gtAbs : \forall (a \, b\, c: Set) (Q_a : a \to Set) (Q_b : b \to Set) (Q_c : c \to Set) 
      (e : Equal\, a\, (b \to c)) (s : String)} \\ 
    %
    \mathsf{ (T_b : LType\, b) (t_c : LTerm \, c)
      \to Equal^{\wedge}\, a\, (b \to c)\, Q_a\, (Arr^{\wedge}\, b\, c\, Q_b\, Q_c)\, e
      \to LType^{\wedge} \, b\, Q_b\, T_b} \\ 
    %
    \mathsf{
      \to Maybe\, (LType\,c) \to Maybe\, (LType\, a)}
\end{multline*}

% app 
\begin{multline*}
    \mathsf{gtApp : \forall (a \, b : Set) (Q_a : a \to Set) (Q_b : b \to Set) 
      (t_{ba} : LTerm\, (b \to a)) (t_b : LTerm\, b)} \\ 
    \mathsf{
      \to Maybe\, (LType\, (b \to a))
      \to Maybe\, (LType\, b)
      \to Maybe\, (LType\, a)
    }
\end{multline*}

% list 
\begin{multline*}
    % abs
    \mathsf{gtListC : \forall (a \, b : Set) (Q_a : a \to Set) (Q_b : b \to Set) 
      (e : Equal\, a\, (List\, b)) (ts : List\, (LTerm\, b))} \\ 
    \mathsf{
      \to Equal^{\wedge}\, a\, (List\,b) \, Q_a\, (List^{\wedge}\, b\, Q_b)\, e
      \to List^{\wedge}\, (LTerm\, b)\, (getType\, b)\, ts
      \to Maybe\, (LType\, a)
    }
\end{multline*}

For variables we simply return the type $\mathsf{T_a}$ given in $\mathsf{Var\, s\, T_a}$, 
and the cases for abstraction and application are similar.
The interesting case is $\mathsf{gtListC}$, in which we have to use 
the results of ($\mathsf{List^{\wedge}\, (LTerm\, b)\, (getType\, b)\, ts}$)
in order to extract the type of one of the terms in the list. 
To define $\mathsf{gtListC}$ we pattern-match on the list of terms $\mathsf{ts}$.

If $\mathsf{ts}$ is the empty list (denoted by $\mathsf{[]}$), we cannot extract a type, 
so we return $\mathsf{nothing}$. \\
{\color{red} Maybe handle this case differently, by using non-empty lists, for example}
\[
  \mathsf{gtListC\, a\, b\, Q_a\, Q_b\, e\, [] \, L_e L_{ts} = nothing}
\]

If $\mathsf{ts}$ is a non-empty list, we pattern match on $\mathsf{L_{ts}}$ and use the result
to construct the type we need:
\begin{align*}
  &\mathsf{gtListC\, a\, b\, Q_a\, Q_b\, e\, (t :: ts) \, L_e (nothing , L_{ts}) = nothing} \\
  &\mathsf{gtListC\, a\, b\, Q_a\, Q_b\, e\, (t :: ts) \, L_e (just\, T_b , L_{ts}) = just \, (TList\, b\, e\, T_b)}
\end{align*}

where $\mathsf{e : Equal\, a\, (List\,b)}$ and $\mathsf{T_b : LType\, b}$.

The last piece of infrastructure we need to define $\mathsf{getTypeProof}$ is a function 
\[
  \mathsf{LTerm^{\wedge}K1 : \forall (a : Set) (t : LTerm A) \to LTerm^{\wedge}\, a\, K1\,t}
\]
that provides a 
proof of $\mathsf{LTerm^{\wedge}\,a\,K1\,t}$ for any term $\mathsf{t : LTerm\, a}$. 
Because $\mathsf{LTerm^{\wedge}}$ is defined in terms of $\mathsf{LType^{\wedge}}$, $\mathsf{Arr^{\wedge}}$, 
and $\mathsf{List^{\wedge}}$, we will need analogous functions for these liftings as well.

{\color{red} Finish example by defining $\mathsf{LTerm^{\wedge}K1}$}
